A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-03-16 main.tex
Updates from Overleaf

%discussion: the third limitation
There are eighty-one ($X_1 ... X_81$) physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, 
% since it has comprehensive clinical features, 
such as age, gender, residual tumor, vital status, days\_to\_last\_followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
However, the TCGA did not collect other features from holistic cancer care.
% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021} spiritual and emotional condition is equally essential comparing with physical and social status.
%
World Health Organisation has called worldwide for delivering people-centred (or person-centred) care from the physical, emotional, socioeconomic, and spiritual perspectives\cite{WHO2015}\cite{Ling-ChengMong2021}.
Core principles can be taken to achieve people-centred and integrated health service delivery. 
The first principle is holistic – focusing on physical, socioeconomic, mental, and emotional well-being. 
Holistic care has been defined that care and sees the person as a whole with psychological, social, and environmental levels of needs and goals.
%that considers  factors rather than just the symptoms of disease or ill-health.
The second principle is empowering – supporting people to manage and take responsibility for their health,
%Empowerment: the process of supporting people and communities to take control of their own health needs resulting, 
for example, in the uptake of healthier behaviors or the ability to self-manage illnesses.
People-centred care requires that people have the education and support they need to make decisions and participate in their care.
%Glossary:
%People-centred care: an approach to care that consciously adopts individuals’, carers’, families’ and communities’ perspectives as participants in, and beneficiaries of, trusted health systems that respond to their needs and preferences in humane and holistic ways. People-centred care also requires that people have the education and support they need to make decisions and participate in their own care. It is organized around the health needs and expectations of people rather than diseases (7,8) 
%Person-centred care: care approaches and practices that see the person as a whole with many levels of needs and goals, with these needs coming from their own personal social determinants of health.
%(1. World Health Organization. WHO global strategy on people-centred and integrated health services: interim report. https://apps.who.int/iris/handle/10665/155002 (2015).)

@@

%%%% PCA and ECA: the way to delivery of MBSR
The therapeutic relationship is essential towards spiritual care.
According to clinical experience in healthcare, sometimes patients could tell the physicians: "How amazing it is. I want to talk about myself more when I visit this doctor whom I trust."
In 1979, Rogers wrote: "I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing. Then simply my presence is releasing and helpful."\cite{Rogers1979}
Carl Rogers developed person-centered theory that the therapist is providing the appropriate social-environmental conditions for their patients\cite{Rogers1957}\cite{Joseph2004}\cite{Griffiths2013}.
Person-centred theory holds that the innate tendency towards growth and development is facilitated by the six conditions described by Rogers in 1957\cite{Rogers1957}:\\
%For constructive personality change to occur, it is necessary that these conditions exist and continue over a period of time: 
1. Two persons are in psychological contact. \\
2. The first, whom we shall term the client, is in a state of incongruence (or not harmony), being vulnerable or anxious. \\
3. The second person, whom we shall term the therapist, is congruent
or integrated with the relationship. \\
4. The therapist experiences "unconditional positive regard" for the client. \\
5. The therapist experiences an empathic understanding of the client's
internal frame of reference and endeavors to communicate this experience to the client. \\
6. The communication to the client of the therapist's empathic understanding and unconditional positive regard is to a minimal degree achieved.\\
%empowering
%(一)雙方有心理的接觸。
%(二)當事人正感到焦慮或不一致(incongruence)。 
%(三)治療者在治療關係中是一致的 (congruence, agreement or harmony; compatibility)、真實的或真誠的。
%(四)治療者能夠對當事人表現出無條件的關懷。無條件關懷(不批判/頓悟)
%(五)治療者能夠同理的瞭解當事人的內在，並努力傳達「我懂你的」。
%(六) 第五點只要有個適當的開始，療癒就會開始
%Dealing with negative emotions. 情緒影響，造成焦慮、發炎、免疫 Cancer
As the cancer patient feels intense negative emotions of extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, 
%七情: 喜、怒、思、悲、恐、驚、憂
depression, fatigue, stress, it is not the patient-centred therapist’s task to remove these feelings: the task is to stay with the patient’s experiences. 
% 只是陪伴
%The research implication is to investigate the necessity and sufficiency of the six conditions.
%Rogers, C. R. A Theory of Therapy, Personality, and Interpersonal Relationships: As Developed in the Client-centered Framework. in Psychology: A Study of a Science. Study 1, Volume 3: Formulations of the Person and the Social Context (ed. Koch, S.) 184–256 (McGraw Hill, 1959).\cite{Rogers1959}
%PCA理論 by *** Tex Chi
%治療關係的六核心條件: 說好話 眼對眼 engaging 用真心
%以心印心 engaging
%身心相連 body-mind connection
%捨末求本 find the source: emotion
Holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection. Their empathy, sympathy, and compassion are induced by the suffering of patients from those diseases. They will try to treat patients by prescribing medicine (and "themselves") or performing surgery.
Thus, the healing resilience of patients will be induced by unconditional positive regard. % of healing.
The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner.
%身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
%「把自己當藥方開出去」
%Spirituality
%慈悲心 compassion 
%同情心 sympathy
%同理心 empathy
%non-verbal contact

@@

%% why holistic? % Environment 環境 => 分享權力、 自決 empowering
The WHO's second principle is empowering – supporting people to manage and take responsibility for their health.
Bruce Lipton introduced mind-brain-body system in 1992\cite{Mokhtari2011}\cite{Kobisi2012}\cite{Gustafson2017}.
%Lipton 1992, epinephrine and histamine signals in endothelium, %心智作用
In a state of fear, the brain releases chemicals of stress hormones and inflammatory cytokines.
Conversely, dopamine, oxytocin, vasopressin, and growth hormone will be released by the central nervous system in response to the perception of love.
%Bruce Lipton: the biology of belief %信念的力量 \cite{Lipton2015}
%placebo effect and the old belief of genetic determinism\cite{Mokhtari2011}\cite{Kobisi2012}\cite{Gustafson2017}
%biowell 勿膨脹自我: 我非常擔心，所謂的科學實驗，研究的疾病，發明的藥物，都會潛藏一種危機，因為它的療效與科學證據，都是建立在「意識統一場域」中，科學家在研究時，一定希望有效，能夠發現別人沒有發現且有用的事情，所以「成功」還是會帶有「人為的意念」。
%那麼，這個結果不「公正」。甚至，當原來藥物發明者的心念改變了，（開始只想賺錢），那麼藥物的作用就更無法掌握。也許，藥物副作用會很嚴重。而目前科學的解釋是，只是因為個體的基因差異。
%% 1. Kobisi, W. Mind inhibitors. in The 30th International Congress Of The World Federation Of Hemophilia, July 8‐12 vol. 18 170–171 (John Wiley & Sons, Ltd, 2012).
%As a person with hemophilia (PWH), my passion led me to conduct personal research to uncover the main cause of my drawbacks in my education, my career, and my romantic life. I have experienced unjustified conflicts in my social relations, feeling stale in mind and body
%Findings: Through my research, I uncovered that I used to suffer from what I call 'mind inhibitors' these were the hidden cause of my life disorders and spontaneous bleeds. These mind inhibitors are responsible for locking the body factor receptors, blocking body energy centres (like the solar plexus), discouraging the super-intelligent body cells from running their auto-healing system, and paralyzing the instinctive high-speed cellular response to external molecular treatment. 
%Mind inhibitors originate from different sources like thinking of oneself in a victim role, anxiety about medical treatments, lack of financial stability, negative attitudes, self-rejection, and contradictory thoughts and feelings. 
%Conclusion: Mind inhibitors should be handled as seriously as biological inhibitors. As Dr. Bruce Lipton explains in his book, 'The Biology of Belief'\cite{Lipton2015}: DNA does not control our biology; instead DNA is controlled by signals from outside the cell. Our bodies can be changed as we retrain our thinking, since thoughts are made of energy that affects the cellular energy level, and thus everything is created twice: once in our minds and then the physical creation follows. % 萬法唯心造
Holistic healthcare should be considered for treating patients as a complete synchronized system of soul, mind, and body; treatment should include more than medication or surgery, but a holistic approach would also address the patient's need for a subconscious paradigm shift in the person's thought and belief system.\cite{Kobisi2012}\cite{Lipton2015}

@@

Epigenetics control says that genetic expression is directly due to the environment of our cells and our perception of the environment\cite{Gustafson2017}.

@@

The mind-brain-body axis shows that subconscious fear causes releasing of inflammatory and stress hormones from the brain in terms of cell alteration in DNA methylation, mutation, mRNA expression. Carcinogenesis will occur if the reprogramming is persistent for a longer time.

@@

In personal history section of admission note for inpatient:\\
<Habits>\\
-Tobacco: \underline{ }\underline{ } pack/day for \underline{ }\underline{ } years\\
-Alcohol drinking: Occasionally\\
-Betel nuts: \underline{ }\underline{ } nuts/day for \underline{ }\underline{ } years\\
<Social/Economic Evaluation>\\
-Living condition: Living with family\\
-Family support: Well\\
-Main caregiver: Spouse\\
-Financial support: Sufficient\\
<Psychological Evaluation>\\
Stable but worry about this oral lesion\\
Suspected to be abuse or neglected victim: negative\\
<Spiritual Assessment>\\
Religion: Nil\\
Diagnosed with life-threatening diseases or terminal stage of chronic diseases or cancers? No\\
% cancer cure (care) 的證明
%# 懺悔
We continually educate our cancer patients that they should repentantly confess for not taking care of body and spirit in the past, and sincere thanks for our physical body does hard work. Mindfulness and meditation will be helpful in cancer healthcare.
Once the holistic feature is available, a graph convolutional neural network (GCNN) is mandatory for further survival analysis\cite{Ching2018a}.
The microenvironment of HNSCC, influenced by the mind-brain-body axis, requires further exploration and understanding using this multi-parametric approach.
%  extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, depression, fatigue, stress
%七情: 喜、怒、思、悲、恐、驚、憂

%*** make Figure 5 holistic: Figure_5_holisticCare.pdf
\begin{figure}[hp]
\centering
\includegraphics[width=14cm]{Figure_5_holisticCare.pdf}
\bcaption{The concept of holistic care for \acrshort{hnscc} patients.}
{Beyond carcinogenesis - Under the mind-brain-body axis, a stressful environment will trigger emotional reception. The subconscious mind (brain) will release stress hormones and inflammation signals in response to the emotion. The physical body's internal environment (cells) alters epigenetic control in gene regulation and mRNA expression. In a long incubation time, the tissue/cells will be transformed into dysplasia then malignancy with helping from known carcinogens.\\
Cancer care - Holistic care should take care of cancer patients' spiritual, emotional, physical, and socioeconomic needs. Physical care will be carried out by medication therapy or surgery. After establishing a therapeutic relationship, the physicians' spiritual properties (empathy, sympathy, and compassion) will engage their patients and recover their self-compassion to gain resilience against the disease.\\
Suggested health care record - Besides physical, pathological, or psychological data, electric healthcare records (EHR) and \acrshort{tcga} should collect "holistic features".}
\label{fig:figure5}
\end{figure}
%meridian and emotion has mutual reaction
%meridian effect tissue and organ
%(autonomic nerve system, myofascial network, prefrontal cortex)
%placebo-effect influence on drug discovery
%gene expression in deep learning
%Ching, T. et al. Opportunities and obstacles for deep learning in biology and medicine. J. R. Soc. Interface 15, (2018).
%慈悲心 利他心
%博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的
%#正念 除了可以減壓，還可以治癒疼痛
% modify the dark environment 改造患者的心，就能改造他的身體環境，有利消除癌症

>>>>

%discussion: the third limitation
There are eighty-one ($X_1 ... X_81$) physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, 
% since it has comprehensive clinical features, 
such as age, gender, residual tumor, vital status, days\_to\_last\_followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
However, the TCGA did not collect other features from holistic cancer care.
% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021} spiritual and emotional condition is equally essential comparing with physical and social status. (see Figure \ref{fig:figure5})
%
World Health Organisation has called worldwide for delivering people-centred (or person-centred) care from the physical, emotional, socioeconomic, and spiritual perspectives\cite{WHO2015}\cite{Ling-ChengMong2021}.
Core principles can be taken to achieve people-centred and integrated health service delivery. 
The first principle is holistic – focusing on physical, socioeconomic, mental, and emotional well-being. 
Holistic care has been defined that care and sees the person as a whole with psychological, social, and environmental levels of needs and goals.
%that considers  factors rather than just the symptoms of disease or ill-health.
The second principle is empowering – supporting people to manage and take responsibility for their health,
%Empowerment: the process of supporting people and communities to take control of their own health needs resulting, 
for example, in the uptake of healthier behaviors or the ability to self-manage illnesses.
People-centred care requires that people have the education and support they need to make decisions and participate in their care.
%Glossary:
%People-centred care: an approach to care that consciously adopts individuals’, carers’, families’ and communities’ perspectives as participants in, and beneficiaries of, trusted health systems that respond to their needs and preferences in humane and holistic ways. People-centred care also requires that people have the education and support they need to make decisions and participate in their own care. It is organized around the health needs and expectations of people rather than diseases (7,8) 
%Person-centred care: care approaches and practices that see the person as a whole with many levels of needs and goals, with these needs coming from their own personal social determinants of health.
%(1. World Health Organization. WHO global strategy on people-centred and integrated health services: interim report. https://apps.who.int/iris/handle/10665/155002 (2015).)

@@

%%%% PCA and ECA: the way to delivery of MBSR
The therapeutic relationship is essential towards spiritual care.
According to clinical experience in healthcare, sometimes patients could tell the physicians: "How amazing it is. I want to talk about myself more when I visit this doctor whom I trust."
In 1979, Rogers wrote: "I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing. Then simply my presence is releasing and helpful."\cite{Rogers1979}
Carl Rogers developed person-centered theory that the therapist is providing the appropriate social-environmental conditions for their patients\cite{Rogers1957}\cite{Joseph2004}\cite{Griffiths2013}.
Person-centred theory holds that the innate tendency towards growth and development is facilitated by the six conditions described by Rogers in 1957\cite{Rogers1957}:\\
%For constructive personality change to occur, it is necessary that these conditions exist and continue over a period of time: 
1. Two persons are in psychological contact. \\
2. The first, whom we shall term the client, is in a state of incongruence (or not harmony), being vulnerable or anxious. \\
3. The second person, whom we shall term the therapist, is congruent
or integrated with the relationship. \\
4. The therapist experiences "unconditional positive regard" for the client. \\
5. The therapist experiences an empathic understanding of the client's
internal frame of reference and endeavors to communicate this experience to the client. \\
6. The communication to the client of the therapist's empathic understanding and unconditional positive regard is to a minimal degree achieved.\\
%empowering
%(一)雙方有心理的接觸。
%(二)當事人正感到焦慮或不一致(incongruence)。 
%(三)治療者在治療關係中是一致的 (congruence, agreement or harmony; compatibility)、真實的或真誠的。
%(四)治療者能夠對當事人表現出無條件的關懷。無條件關懷(不批判/頓悟)
%(五)治療者能夠同理的瞭解當事人的內在，並努力傳達「我懂你的」。
%(六) 第五點只要有個適當的開始，療癒就會開始
%Dealing with negative emotions. 情緒影響，造成焦慮、發炎、免疫 Cancer
As the cancer patient feels intense negative emotions of extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, 
%七情: 喜、怒、思、悲、恐、驚、憂
depression, fatigue, stress, it is not the patient-centred therapist’s task to remove these feelings: the task is to stay with the patient’s experiences. 
% 只是陪伴
%The research implication is to investigate the necessity and sufficiency of the six conditions.
%Rogers, C. R. A Theory of Therapy, Personality, and Interpersonal Relationships: As Developed in the Client-centered Framework. in Psychology: A Study of a Science. Study 1, Volume 3: Formulations of the Person and the Social Context (ed. Koch, S.) 184–256 (McGraw Hill, 1959).\cite{Rogers1959}
%PCA理論 by *** Tex Chi
%治療關係的六核心條件: 說好話 眼對眼 engaging 用真心
%以心印心 engaging
%身心相連 body-mind connection
%捨末求本 find the source: emotion
Holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection. Their empathy, sympathy, and compassion are induced by the suffering of patients from those diseases. They will try to treat patients by prescribing medicine (and "themselves") or performing surgery.
Thus, the healing resilience of patients will be induced by unconditional positive regard. % of healing.
The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner. (see Figure \ref{fig:figure5})
%身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
%「把自己當藥方開出去」
%Spirituality
%慈悲心 compassion 
%同情心 sympathy
%同理心 empathy
%non-verbal contact

@@

%% why holistic? % Environment 環境 => 分享權力、 自決 empowering
The WHO's second principle is empowering – supporting people to manage and take responsibility for their health.
Bruce Lipton introduced mind-brain-body system in 1992\cite{Mokhtari2011}\cite{Kobisi2012}\cite{Gustafson2017}.
%Lipton 1992, epinephrine and histamine signals in endothelium, %心智作用
In a state of fear, the brain releases chemicals of stress hormones and inflammatory cytokines.
Conversely, dopamine, oxytocin, vasopressin, and growth hormone will be released by the central nervous system in response to the perception of love.
% Arginine vasopressin (AVP) and oxytocin (OXT) are two centrally released neuropeptides that are involved in shaping essential social behaviors, like aggression, social recognition, and social motivation.
%Bruce Lipton: the biology of belief %信念的力量 \cite{Lipton2015}
%placebo effect and the old belief of genetic determinism\cite{Mokhtari2011}\cite{Kobisi2012}\cite{Gustafson2017}
%biowell 勿膨脹自我: 我非常擔心，所謂的科學實驗，研究的疾病，發明的藥物，都會潛藏一種危機，因為它的療效與科學證據，都是建立在「意識統一場域」中，科學家在研究時，一定希望有效，能夠發現別人沒有發現且有用的事情，所以「成功」還是會帶有「人為的意念」。
%那麼，這個結果不「公正」。甚至，當原來藥物發明者的心念改變了，（開始只想賺錢），那麼藥物的作用就更無法掌握。也許，藥物副作用會很嚴重。而目前科學的解釋是，只是因為個體的基因差異。
%% 1. Kobisi, W. Mind inhibitors. in The 30th International Congress Of The World Federation Of Hemophilia, July 8‐12 vol. 18 170–171 (John Wiley & Sons, Ltd, 2012).
%As a person with hemophilia (PWH), my passion led me to conduct personal research to uncover the main cause of my drawbacks in my education, my career, and my romantic life. I have experienced unjustified conflicts in my social relations, feeling stale in mind and body
%Findings: Through my research, I uncovered that I used to suffer from what I call 'mind inhibitors' these were the hidden cause of my life disorders and spontaneous bleeds. These mind inhibitors are responsible for locking the body factor receptors, blocking body energy centres (like the solar plexus), discouraging the super-intelligent body cells from running their auto-healing system, and paralyzing the instinctive high-speed cellular response to external molecular treatment. 
%Mind inhibitors originate from different sources like thinking of oneself in a victim role, anxiety about medical treatments, lack of financial stability, negative attitudes, self-rejection, and contradictory thoughts and feelings. 
%Conclusion: Mind inhibitors should be handled as seriously as biological inhibitors. As Dr. Bruce Lipton explains in his book, 'The Biology of Belief'\cite{Lipton2015}: DNA does not control our biology; instead DNA is controlled by signals from outside the cell. Our bodies can be changed as we retrain our thinking, since thoughts are made of energy that affects the cellular energy level, and thus everything is created twice: once in our minds and then the physical creation follows. % 萬法唯心造
Holistic healthcare should be considered for treating patients as a complete synchronized system of soul, mind, and body; treatment should include more than medication or surgery, but a holistic approach would also address the patient's need for a subconscious paradigm shift in the person's thought and belief system.\cite{Kobisi2012}\cite{Lipton2015}

@@

Epigenetics control says that genetic expression is directly due to the environment of our cells and our perception of the environment\cite{Gustafson2017}. (see Figure \ref{fig:figure5})

@@

The mind-brain-body axis shows that subconscious fear causes releasing of inflammatory and stress hormones from the brain in terms of cell alteration in DNA methylation, mutation, mRNA expression. Carcinogenesis will occur if the reprogramming is persistent for a longer time. (see Figure \ref{fig:figure5})

@@

In personal history section of admission note for inpatient:\\
<Habits>\\
-Tobacco: \underline{ }\underline{ } pack/day for \underline{ }\underline{ } years\\
-Alcohol drinking: Occasionally\\
-Betel nuts: \underline{ }\underline{ } nuts/day for \underline{ }\underline{ } years\\
<Social/Economic Evaluation>\\
-Living condition: Living with family\\
-Family support: Well\\
-Main caregiver: Spouse\\
-Financial support: Sufficient\\
<Psychological Evaluation>\\
Stable but worry about this oral lesion\\
Suspected to be abuse or neglected victim: negative\\
<Spiritual Assessment>\\
Religion: Nil\\
Diagnosed with life-threatening diseases or terminal stage of chronic diseases or cancers? No\\
% cancer cure (care) 的證明
%# 懺悔
We continually educate our cancer patients that they should repentantly confess for not taking care of body and spirit in the past, and sincere thanks for our physical body's hard working. Mindfulness and meditation will be helpful in cancer healthcare.
Once the holistic feature is available, a graph convolutional neural network (GCNN) is mandatory for further survival analysis\cite{Ching2018a}.
The microenvironment of HNSCC, influenced by the mind-brain-body axis, requires further exploration and understanding using this multi-parametric approach.
%  extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, depression, fatigue, stress
%七情: 喜、怒、思、悲、恐、驚、憂

%*** make Figure 5 holistic: Figure_5_holisticCare.pdf
\begin{figure}[hp]
\centering
\includegraphics[width=14cm]{Figure_5_holisticCare.pdf}
\bcaption{The concept of holistic care for \acrshort{hnscc} patients.}
{\\Beyond carcinogenesis - Under the mind-brain-body axis, a stressful environment will trigger emotional reception. The subconscious mind (brain) will release stress hormones and inflammation signals in response to the emotion. The physical body's internal environment (cells) alters epigenetic control in gene regulation and mRNA expression. In a long incubation time, the tissue/cells will be transformed into dysplasia then malignancy with helping from known carcinogens.\\
Cancer care - Holistic care should take care of cancer patients' spiritual, emotional, physical, and socioeconomic needs. Physical care will be carried out by medication therapy or surgery. After establishing a therapeutic relationship, the physicians' spiritual properties (empathy, sympathy, and compassion) will engage their patients and recover their self-compassion to gain resilience against the disease.\\
Suggested health care record - Besides physical, pathological, or psychological data, electric healthcare records (EHR) and \acrshort{tcga} should collect "holistic features".}
\label{fig:figure5}
\end{figure}
%meridian and emotion has mutual reaction
%meridian effect tissue and organ
%(autonomic nerve system, myofascial network, prefrontal cortex)
%placebo-effect influence on drug discovery
%gene expression in deep learning
%Ching, T. et al. Opportunities and obstacles for deep learning in biology and medicine. J. R. Soc. Interface 15, (2018).
%慈悲心 利他心
%博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的
%#正念 除了可以減壓，還可以治癒疼痛
% modify the dark environment 改造患者的心，就能改造他的身體環境，有利消除癌症
